\emph{icepack}: a novel glacier flow modeling package

### 2020-12-09 icepack.tex
Add line numbers
Show ice volume from MISMIP

\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{amsthm}
%\usepackage{amssymb}
%\usepackage{mathrsfs}
%\usepackage{fullpage}
%\usepackage{mathptmx}
%\usepackage[varg]{txfonts}
\usepackage{natbib}
\usepackage{color}
\usepackage[charter]{mathdesign}
\usepackage[pdftex]{graphicx}
%\usepackage{float}
%\usepackage{hyperref}
%\usepackage[modulo, displaymath, mathlines]{lineno}
%\usepackage{setspace}
%\usepackage[titletoc,toc,title]{appendix}

%\linenumbers
%\doublespacing

@@

Figure \ref{fig:mismip} shows the outcome of the MISMIP+ experiment performed using icepack.

\begin{figure}[h]
    \includegraphics[width=0.95\linewidth]{demos/mismip/steady-state.png}
    \caption{The steady state thickness and velocity of the MISMIP+ experimental setup with the Weertman sliding law.}
    \label{fig:mismip}
\end{figure}

>>>>

\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{amsthm}
%\usepackage{amssymb}
%\usepackage{mathrsfs}
%\usepackage{fullpage}
%\usepackage{mathptmx}
%\usepackage[varg]{txfonts}
\usepackage{natbib}
\usepackage{color}
\usepackage[charter]{mathdesign}
\usepackage[pdftex]{graphicx}
%\usepackage{float}
%\usepackage{hyperref}
%\usepackage[modulo, displaymath, mathlines]{lineno}
%\usepackage{setspace}
%\usepackage[titletoc,toc,title]{appendix}
\usepackage{lineno}
\linenumbers
%\doublespacing

@@

Figure \ref{fig:mismip-result} shows the thickness and ice speed after spinning up the MISMIP+ geometry and input data to steady state with the sliding law described above.
The spin-up used used degree-1 basis functions for both thickness and velocity.
To get a high-resolution estimate for the steady state, the spin-up started from a relatively coarse resolution to propagate out most of the transient signal.
Then the mesh was successively refined and spun up again to propagate out the remaining high-wavenumber transients.
This process was repeated three times.
The net result is that most of the spin-up is done at relatively little computational cost.
Figure \ref{fig:mismip-volumes} shows the total ice mass during the retreat and readvance phases of the experiment.
The initial response to turning on melting is very rapid but then becomes roughly linear with time.
When the high melt is turned off at the 100-year mark, the ice readvances, but the rate is much slower than the rate of decrease when melt was on.
This asymmetric response is typical and expected from ice physics.

\begin{figure}[h]
    \includegraphics[width=0.95\linewidth]{demos/mismip/steady-state-result.png}
    \caption{The steady state thickness and velocity of the MISMIP+ experimental setup with the Weertman sliding law.}
    \label{fig:mismip-result}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=0.5\linewidth]{demos/mismip/volumes.png}
    \caption{Total ice mass history during retreat (first 100 years) and readvance (second 100 years) of MISMIP+ experiment.}
    \label{fig:mismip-volumes}
\end{figure}
